---
output: 
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# MicrobiotaProcess: an R package for analysis, visualization and biomarker discovery of microbiome

```{r, echo=FALSE, results="hide", message=FALSE}
Biocpkg <- function (pkg) {
    sprintf("[%s](http://bioconductor.org/packages/%s)", pkg, pkg)
}
```

```{r comment="", echo=FALSE, results='asis'}
cat(packageDescription('MicrobiotaProcess')$Description)
```

## :writing_hand: Authors

[Shuangbin Xu](https://github.com/xiangpin) and [Guangchuang Yu](https://guangchuangyu.github.io)

School of Basic Medical Sciences, Southern Medical University

## :arrow_double_down: Installation

Get the released version from [Bioconductor](https://bioconductor.org/packages/release/bioc/html/MicrobiotaProcess.html):

```r
## try http:// if https:// URLs are not supported ## the url of mirror
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")
## BiocManager::install("BiocUpgrade") ## you may need this
BiocManager::install("MicrobiotaProcess")
```

the development version from github:

```r
if (!requireNamespace("remotes", quietly=TRUE))
    install.packages("remotes")
remotes::install_github("YuLab-SMU/MicrobiotaProcess")
```

## :sparkling_heart: Contributing

We welcome any contributions! By participating in this project you agree to bide 
by the terms outlined in the [Contributor Code of Conduct](CONDUCT.md).
